[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper update

## Same-Sex 
# Discussion {#sec-discussion}
## First discussion point {#sec-first-point}
## Second discussion point
## Third discussion point
## Weaknesses and Future Research {#sec-future}

>>>>

# Discussion {#sec-discussion}
## First discussion point {#sec-first-point}
## Second discussion point
## Third discussion point
## Weaknesses and Future Research {#sec-future}
